---
title             : "Creating APA-style papers with the R package papaja"
shorttitle        : "Writing with papaja"

author: 
  - name          : "Iris Zhong"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author

affiliation:
  - id            : "1"
    institution   : "Stanford University"


abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "references.bib", "manual-reference.bib"]

floatsintext      : no
linenumbers       : no
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_doc
---

```{r setup, include = FALSE}
library("papaja")
library("tidyverse")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction

Some introduction

# Background

Here's a citation from the manual bibliography: @isnandar2022effect

# Methods

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

xxx

## Material

xxx

### Data A

xxx

Here's one citation from zotero: @2010cen


### Data B

xxx

## Procedure

xxxx

## Data analysis

We used `r cite_r("r-references.bib")` for all our analyses.

# Results

```{r}
x <- c(1, 4, 6, 7, 10) + 1
```

The mean of x is `r mean(x)`.

```{r}
y <- c(5, 8, 6, 10, 15)
```

```{r}
mod <- lm(y ~ x)
coef_mod <- coefficients(mod) # extract coefficients
coef_mod
```

The predicted model is $y = `r coef_mod[1]`+`r coef_mod[2]` x$

# Discussion

xxxx

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
